---
title: "Lab 03"
author: "Joud AlFarra"
date: "Tuesday May, 2, 2023"
output:
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

# Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
``` 

# Data

```{r load-data, message = FALSE}
fl_votes <- st_read("data/fl_votes.shp", quiet = TRUE)
fl_votes %>%
  slice(1:6)
```

# Exercise 1

```{r add-winner}
fl_votes <- fl_votes %>% mutate(winner20 = if_else(rep20 > dem20, "Donald Trump", "Joe Biden"))
```

# Exercise 2

```{r fl-plot-1}
ggplot(fl_votes) +
  geom_sf(aes(fill = winner20)) +
  scale_fill_manual(values = c("#DE0100", "#0015BC")) +
  labs(title = "Election Winners 2020", fill = "Winner") +
  theme_bw()
```

# Exercise #3

```{r fl-props}
fl_votes <- fl_votes %>% mutate(Prop_rep16 = rep16 / (rep16 + dem16),
                                Prop_rep20 = rep20 / (rep20 + dem20))
```

# Exercise 4

```{r fl-plot-2}
ggplot(fl_votes) +
  geom_sf(aes(fill = Prop_rep20)) +
  scale_fill_gradient(low = "#0015BC", high = "#DE0100") +
  labs(title = "Election 2020 Results", fill = "Republican Share of Votes") +
  theme_bw()
```

# Exercise 5

```{r fl-change}
fl_votes <- fl_votes %>% mutate(diff_rep = Prop_rep20 - Prop_rep16)
```

# Exercise 6

```{r fl-plot-3}
ggplot(fl_votes) +
  geom_sf(aes(fill = diff_rep)) +
  scale_fill_gradient2(low = "#0015BC", midpoint = 0, high = "#DE0100") +
  labs(title = "Change in Republican Vote Share Between 2016 and 2020", fill = "Change in Republican Share") +
  theme_bw()
```

# Exercise 7

-What do the visualizations you developed tell you about the 2016 and 2020 Presidential election in Florida? What are limitations of these visualizations?

The visualizations show that even though the republicans won the 2020 elections, the proportions of the republican party to the democratic party is very close. 
Limitations of the visualization could be the closeness in shades of colors, which might cause inaccuracy when reading the data.
